[dcpo_demsupport]

### 2020-07-03 paper/dcpo_demsupport_appendix.Rmd
add chunks for dcpo_input_raw and dcpo_input; move replication to appendix

claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
                              col_types = "cdcddcd") %>%           # 1578 obs
    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
           project = case_when(p_dcpo == "afrob" ~ "afb",
                               p_dcpo == "amb" ~ "lapop",
                               p_dcpo == "arabb" ~ "arb",
                               p_dcpo == "asiab" ~ "asb",
                               p_dcpo == "asianb" ~ "asnb",
                               p_dcpo == "neb" ~ "ndb",
                               p_dcpo == "sasianb" ~ "sab",
                               TRUE ~ p_dcpo),
           y_dcpo = year) %>%
    dplyr::select(country, year, y_dcpo, survey, project) %>% 
    unique()

>>>>

claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
                              col_types = "cdcddcd") %>%           # 1784 obs
    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
           project = case_when(p_dcpo == "afrob" ~ "afb",
                               p_dcpo == "amb" ~ "lapop",
                               p_dcpo == "arabb" ~ "arb",
                               p_dcpo == "asiab" ~ "asb",
                               p_dcpo == "asianb" ~ "asnb",
                               p_dcpo == "neb" ~ "ndb",
                               p_dcpo == "sasianb" ~ "sab",
                               TRUE ~ p_dcpo),
           y_dcpo = year) %>%
    dplyr::select(country, year, y_dcpo, survey, project) %>% 
    unique()
